%-------------------------
% Resume in Latex
% Original Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------
% Resume LONG Ver. in Latex
% Author : John Doe
% License : MIT
%------------------------

\documentclass[a4paper,12pt]{article}

%% Packages{{{
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[symbol*]{footmisc}
%\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

%% }}}

%% Settings {{{
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.3in}
\addtolength{\textheight}{1.0in}
\addtolength{\skip\footins}{.3in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
%\pdfgentounicode=1
%% }}}


\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \small #4 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeResearchHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
	  \textit{\small{#3}} & \hspace{-100pt} \textit{\small{#4}} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\ScorelistBegin}{
	Selected Major Courses:\\
	\begin{tabular*}{0.7\textwidth}[t]{l@{\extracolsep{\fill}}r}
	}
\newcommand{\ScorelistEnd}{\end{tabular*}\vspace{-7pt}}
\newcommand{\Scoreitem}[2]{
	\hspace{12pt} -	#1 & #2 \\
}
%% }}}

%%%%%%%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\begin{center}
    \textbf{\Huge Jiahui Zhang} \\ \vspace{5pt} 
    \normalsize{Tel: +86 15986690353, 
    	Email: \href{mailto:holmeszh@qq.com}{\tt\underline{holmeszh@qq.com}} , 
    	Web: \href{https://holmes1204.github.io}{\underline{\tt{https://holmes1204.github.io}}}}\\ 
    	\vspace{3pt} 
\end{center}


\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Harbin Institute of Technology, Shenzhen, China}{Aug. 2019 -- Jun. 2023}
      {Bachelor of Engineering in Automation}{}
	\resumeItemListStart
		\resumeItem{Overall GPA:3.594/4, Overall Score:87.471/100}
		\item \ScorelistBegin
			\Scoreitem{High-level Language Programming}{93.7}
			\Scoreitem{Design and Practice of Robotic System}{89}
			\Scoreitem{Theoretical Mechanics II}{84}
			\Scoreitem{Fundamentals of Machine Design}{85}
			\Scoreitem{Fundamentals of Analog Electronics}{88}
			\Scoreitem{Digital Electronics Technology Foundation}{89}
			\Scoreitem{Signal Analysis and Processing}{88}
			\Scoreitem{System Modeling and Simulation}{93}
			\Scoreitem{Automatic Control Theory A, B}{91,92}
			\Scoreitem{Automatic Control Practice A, B}{84,93}
			\ScorelistEnd
		\resumeItemListEnd
  \resumeSubHeadingListEnd


\section{honors and awards}
\resumeSubHeadingListStart
	\resumeProjectHeading
	{Outstanding Student Scholarship Third Prize}{Nov. 2022}
	\resumeProjectHeading
	{The 20th China University Robot Competition (ROBOCON) Third Prize}{Jul. 2021}
	\resumeProjectHeading
	{School Engineering Training Competition  Second Prize}{Mar. 2021}
	\resumeProjectHeading
	{Excellent Student Cadre}{Dec. 2021}
	\resumeProjectHeading
	{The Robot Developer Competition (RoboCom) First Prize in automatic part}{Dec.  2020}
	\resumeProjectHeading
	{The Robot Developer Competition (RoboCom) Second Prize in semi-automatic part}{Dec. 2020}
	\resumeProjectHeading
	{Outstanding Student Scholarship Third Prize}{Nov. 2021}
	\resumeProjectHeading
	{Mathematical Contest in Modeling Third Prize}{Oct. 2020}
	\resumeProjectHeading
	{Outstanding New Undergraduate Student Third Prize}{Sept. 2019}
\resumeSubHeadingListEnd



\section{research experience}
  \resumeSubHeadingListStart
	\resumeResearchHeading
        {Quadruped Robot Dynamic Grasping Based on WBC}{Mar. 2023 -- Jun. 2023}
        {Supervisor: Prof.Xiaogang Xiong}{School of Mechanical Engineering and Automation}
        \resumeItemListStart
            \resumeItem{Researching on novel high-efficiency robot motion planning algorithms tackling constraints.}
            \resumeItem{Developing an autonomous mobile manipulation platform operating in dynamic environments.}
        \resumeItemListEnd
    \resumeResearchHeading
        {Quadruped Robot Design and Control in RoboCon}{Oct. 2021 -- Aug. 2022}
	    {Supervisor: Prof.Yunjiang Lou, Associate Dean}{School of Mechanical Engineering and Automation}
        \resumeItemListStart
            \resumeItem{Proposed a framework addressing the distributed consensus problem for multi-agent systems with constraints, uncertainties, and time-varying directed topologies.} 
            \resumeItem{Presented distributed consensus algorithms, theoretical proof of convergence, numerical simulations, and physical experiments for validation.}
        \resumeItemListEnd
 \resumeSubHeadingListEnd


\section{selected projects}
    \resumeSubHeadingListStart
      \resumeSubheading
        {Robocon 2021}{Oct. 2020 -- Aug. 2021}
        {Advisors: Prof.Xiaogang Xiong, Prof.Yunjiang Lou, Associate Dean}{HITSZ}
          \resumeItemListStart
            \resumeItem{Developing decision-making modules for a robotic solution to the autonomous trolley collection task at airports. Working on perception-aware planning and multi-robot collaboration.
            }
            \resumeItem{Proposed a safety-critical motion planner prototype for obstacle avoidance and perception-aware planning. 
                Conducted realistic tests and validated the effectiveness of the prototype. 
            }
          \resumeItemListEnd

      \resumeSubheading
        {Hexalink Table Tennis Shooting Manipulator}{Mar. 2022 -- Jun. 2022}
        {Advisor: Prof. Yunjiang Lou, Associate Dean}{HITSZ}
          \resumeItemListStart
            \resumeItem{Designed robot manipulator control algorithms based on the 6-DOF manipulator's forward and inverse kinematics using LFPB trajectory planning.} 
            \resumeItem{Developed a user interface for managing position information of manipulated objects.}
            \resumeItem{Achieved fast palletizing and grasping motions with high accuracy.}
          \resumeItemListEnd
      
	\resumeSubheading
	{RoboCOM}{Oct. 2019 -- Dec. 2019}
	{Advisor: Prof. Xiaogang Xiong}{HITSZ}
	\resumeItemListStart
	\resumeItem{Identified a specific parking sign by adopting traditional vision techniques including filtering, color segmentation, perspective transformation, Canny edge detection, polygon envelope, etc.}
	\resumeItem{Designed an online close-loop controller for a differential-drive autonomous car, employing multiple control schemes and leveraging vision information.}
	\resumeItem{Integrated searching, detection, and motion control with ROS and realized fully automated parking.}
	\resumeItemListEnd
	
	\resumeSubheading
	{Rov underwater}{Oct. 2019 -- Dec. 2019}
	{Advisor: Prof. Xiaogang Xiong}{HITSZ}
	\resumeItemListStart
	\resumeItem{1}
	\resumeItemListEnd
	
	\resumeSubheading
	{Vision-based tracking}{Oct. 2019 -- Dec. 2019}
	{Advisor: Prof. Haoyao Chen}{HITSZ}
	\resumeItemListStart
	\resumeItem{1}
	\resumeItemListEnd
	\resumeSubheading
	{grade one project}{Oct. 2019 -- Dec. 2019}
	{Advisor: Prof. Xiaogang Xiong}{HITSZ}
	\resumeItemListStart
	\resumeItem{1}
	\resumeItemListEnd
    \resumeSubHeadingListEnd


\section{work experience}
\resumeSubHeadingListStart
	\resumeResearchHeading
	{WT Robot-team}{Sept. 2020 -- Aug. 2022}
	{Member of a robotic team}{Harbin Institute of Technology}
	\resumeItemListStart
	\resumeItem{Researching on novel high-efficiency robot motion planning algorithms tackling constraints.}
	\resumeItem{Developing an autonomous mobile manipulation platform operating in dynamic environments.}
	\resumeItemListEnd


	\resumeResearchHeading
	{Innox sz}{Sept. 2022 -- Present}
	{Intern}{Innox sz}
	\resumeItemListStart
	\resumeItem{Proposed a framework addressing the distributed consensus problem for multi-agent systems with constraints, uncertainties, and time-varying directed topologies.} 
	\resumeItem{Presented distributed consensus algorithms, theoretical proof of convergence, numerical simulations, and physical experiments for validation.}
	\resumeItemListEnd
\resumeSubHeadingListEnd

\section{skills}
    \begin{itemize}[leftmargin=3.5mm, label={}]
        \setlength{\itemsep}{0.05em}
        \setlength{\topsep}{1em}
        \item
                \textbf{Languages}{: English (CET4 553/710), Mandarin Chinese (native), Cantonese (native)}
        \item \textbf{Programming}{: C/C++, Python,Shell script}
        \item \textbf{Tools}{: Ubuntu,Git, MATLAB, PyTorch, Ansys, Solidworks, ROS, VS Code, \LaTeX, Eigen} 
    \end{itemize}
    
%\section{Extracurricular Activities}
\section{miscellaneous}
    \resumeSubHeadingListStart
      \resumeProjectHeading
        {\textbf{Athletics}: Left/Right Forward, HITSZ Student Soccer Team}{2017 – 2021}
      \resumeProjectHeading
        {\textbf{Volunteer services}: 2018 Hong Kong Universities and Colleges Forum at HITSZ}{2018}
      \resumeProjectHeading
        {\textbf{\textsl{\small TOEFL iBT}\textsuperscript{\textregistered}}: 
                R30+L30+S28+W29 
         }{2020}
      \resumeProjectHeading
         {\textbf{\textsl{\small GRE}\textsuperscript{\textregistered} General}: 
                V168+Q170+AW5.0
         }{2019}
    \resumeSubHeadingListEnd

\end{document}

